Recent demography drives changes in linked selection across the maize genome

### 2015-11-24 NatGen/manuscript.tex
updates

\subsection*{Diversity is strongly influenced by purifying selection} %JRI

In the case of purifying or background selection, diversity is reduced in functional regions of the genome via removal of deleterious mutations \cite{charlesworth1993}.
We investigated purifying selection in maize and teosinte by evaluating the reduction of diversity around genes.
Pairwise diversity is strongly reduced within genes for both maize and teosinte (Figure \ref{fig:purify}A) but recovers quickly at sites outside of genes, consistent with the low levels of linkage disequilibrium generally observed in these subspecies \cite{tenaillon2002,chia2012}. 
The reduction in relative diversity is more pronounced in teosinte, reaching lower levels in genes and occurring over a wider region.

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{NatureSeriesT}
\bibliography{Reference}
}

>>>>

\subsection*{Diversity is strongly influenced by purifying selection} %JRI
In the case of purifying or background selection, diversity is reduced in functional regions of the genome via removal of deleterious mutations \cite{charlesworth1993}.
We investigated purifying selection in maize and teosinte by evaluating the reduction of diversity around genes.
Pairwise diversity is strongly reduced within genes for both maize and teosinte (Figure \ref{fig:purify}A) but recovers quickly at sites outside of genes, consistent with the low levels of linkage disequilibrium generally observed in these subspecies \cite{tenaillon2002,chia2012}. 
The reduction in relative diversity is more pronounced in teosinte, reaching lower levels in genes and occurring over a wider region.

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{naturemag}
\bibliography{Reference}
}
